E1 Testing - Bayesian Mixed Models

### 2023-09-17 Misc/Visuals_Interactives/tikz_net.qmd
sync

\centering 
\begin{tikzpicture}[shorten >=1pt,->,draw=black!100, node distance=\layersep, scale=1] 
  \tikzstyle{every pin edge}=[<-,shorten <=1pt]; 
  \tikzstyle{neuron}=[circle, draw=black!100, minimum size=17pt,inner sep=0pt]; 
  \tikzstyle{input neuron}=[neuron]; 
  \tikzstyle{output neuron}=[neuron]; 
  \tikzstyle{hidden n

>>>>

\centering 
\begin{tikzpicture}[shorten >=1pt,->,draw=black!100, node distance=\layersep, scale=1] 
  \tikzstyle{every pin edge}=[<-,shorten <=1pt]; 
  \tikzstyle{neuron}=[circle, draw=black!100, minimum size=17pt,inner sep=0pt]; 
  \tikzstyle{input neuron}=[neuron]; 
  \tikzstyle{output neuron}=[neuron]; 
  \tikzstyle{hidden neuron}=[neuron]; 
  \tikzstyle{annot} = [text width=4em, text centered, text=black!100]

  % drawing neurons 
  \foreach \name / \y in {1,...,3} 
      \node [input neuron, pin=left:\textcolor{black!100}{Input \y}] (I-\name) at (0,-0.5-\y) {};
  \foreach \name / \y in {1/1,2/2,3/3,4/4} 
      \path[yshift=0cm] 
          node[hidden neuron] (H-\name) at (1* \layersep,-\y cm) {};
  \foreach \name / \y in {5/1,6/2,7/3,8/4} 
      \path[yshift=0cm] 
          node[hidden neuron] (H-\name) at (2* \layersep,-\y cm) {};
  \foreach \name / \y in {9/1,10/2,11/3,12/4} 
      \path[yshift=0cm] 
          node[hidden neuron] (H-\name) at (3* \layersep,-\y cm) {};
  \node[output neuron,pin={[pin edge={->}]right:\textcolor{black!100}{Output}}, right of=H-10, yshift=-0.5cm] (O) {};

   % drawing arrows 
  \foreach \source in {1,...,3} 
      \foreach \dest in {1,...,4}
           \path (I-\source) edge (H-\dest); 
  \foreach \source in {1,...,4} 
      \foreach \dest in {5,...,8}
           \path (H-\source) edge (H-\dest); 
  \foreach \source in {5,...,8} 
      \foreach \dest in {9,...,12}
           \path (H-\source) edge (H-\dest); 
  \foreach \source in {9,...,12}
           \path (H-\source) edge (O);

   % annotations 
  \node[annot,above of=I-1, node distance=2.5cm] {Input layer}; 
  \node[annot,above of=I-1, node distance=1.5cm] {$\circled{3}$}; 
  \node[annot,above of=H-1, node distance=2cm] (hl1) {Hidden layer 1}; 
  \node[annot,above of=H-1, node distance=1cm] (hl1) {$\circled{4}$}; 
  \node[annot,above of=H-5, node distance=2cm] (hl2) {Hidden layer 2}; 
  \node[annot,above of=H-5, node distance=1cm] (hl2) {$\circled{4}$}; 
  \node[annot,above of=H-9, node distance=2cm] (hl3) {Hidden layer 3}; 
  \node[annot,above of=H-9, node distance=1cm] (hl3) {$\circled{4}$}; 
  \node[annot,above of =O, node distance=3.5cm] {Output layer}; 
  \node[annot,above of =O, node distance=2.5cm] {$\circled{1}$};

### Latent Space Projection
https://tikz.net/manifold/
```{r, engine = 'tikz',engine.opts=list(extra.preamble = c("\\usepackage{cmbright}"))}
#| eval: true
#| cache: true

\usetikzlibrary{arrows.meta}
\definecolor{green}{rgb}{0.0,0.50,0.0}
\tikzset{>={Straight Barb[angle'=80, scale=1.1]}}
\begin{tikzpicture}

\draw[->] (0, 0) -- ++(0, 2);
\draw[->] (0, 0) -- ++(2.5, 0.6);
\draw[->] (0, 0) -- ++(3, 0) node[midway, below, yshift=-0.5em]
    {Original space ${\cal X}$};

\draw[fill=green!50, draw=none, shift={(0.2, 0.7)},scale=0.5]
  (0, 0) to[out=20, in=140] (1.5, -0.2) to [out=60, in=160]
  (5, 0.5) to[out=130, in=60]
  cycle;

\shade[thin, left color=green!10, right color=green!50, draw=none,
  shift={(0.2, 0.7)},scale=0.5]
  (0, 0) to[out=10, in=140] (3.3, -0.8) to [out=60, in=190] (5, 0.5)
    to[out=130, in=60] cycle;

  \draw[->] (4.8, 0.8) -- ++(0, 2);
  \draw[->] (4.8, 0.8) -- ++(2, 0) node[midway, below, yshift=-0.5em]
      {Latent space ${\cal F}$};

  \draw[thin, fill=green!30, draw=none, shift={(5.4, 1.1)}, rotate=20]
    (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- cycle;

  \draw[thick,->,red]
    (1.5, 1.3) to [out=55, in=150] node[midway, above, xshift=6pt, yshift=2pt]
    {$f$} (5.7, 2);

  \draw[thick,->,blue] (1.5, 1.3) ++(4.03, 0.3) to [out=150, in=55]
    node[midway, below, xshift=2pt, yshift=-2pt] {$g$} ++(-3.6, -0.5);

### Flow
https://tikz.net/maf/
```{r, engine = 'tikz'}
#| cache: true

\usetikzlibrary{calc,positioning}

\begin{tikzpicture}[
    thick, text centered,
    box/.style={draw, thin, minimum width=1cm},
    func/.style={circle, text=white},
    input/.style={draw=red, very thick},
  ]

  % x nodes
  \node[box, input, fill=blue!20] (x1) {$x_1$};
  \node[box, input, fill=blue!20, right of=x1] (x2) {$x_2$};
  \node[right of=x2] (xdots1) {\dots};
  \node[box, input, fill=blue!20, right of=xdots1] (xd) {$x_d$};
  \node[box, fill=green!60!black, text opacity=1, opacity=0.4, right=2 of xd] (xdp1) {$x_{d+1}$};
  \node[right of=xdp1] (xdots2) {\dots};
  \node[box, fill=green!60!black, text opacity=1, opacity=0.4, right of=xdots2] (xD) {$x_D$};

  % z nodes
  \node[box, fill=blue!20, below=3 of x1] (z1) {$z_1$};
  \node[box, fill=blue!20, right of=z1] (z2) {$z_2$};
  \node[right of=z2] (zdots1) {\dots};
  \node[box, fill=blue!20, right of=zdots1] (zd) {$z_d$};
  \node[box, input, fill=orange!40, right=2 of zd] (zdp1) {$z_{d+1}$};
  \node[right of=zdp1] (zdots2) {\dots};
  \node[box, fill=orange!40, right of=zdots2] (zD) {$z_D$};

  % z to x lines
  \draw[->] (zdp1) -- (xdp1);

  % scale and translate functions
  \node[func, font=\large, fill=teal, above right=0.1] (t) at ($(zd)!0.5!(xdp1)$) {$t$};
  \fill[teal, opacity=0.5] (x1.south west) -- (t.center) -- (xd.south east) -- (x1.south west);

  \node[func, font=\large, fill=orange, below left=0.1] (s) at ($(zd)!0.5!(xdp1)$) {$s$};
  \fill[orange, opacity=0.5] (x1.south west) -- (s.center) -- (xd.south east) -- (x1.south west);

  % feeding in s and t
  \node[func, inner sep=0, fill=orange] (odot1) at ($(zdp1)!0.4!(xdp1)$) {$\odot$};
  \node[func, inner sep=0, fill=teal] (oplus1) at ($(zdp1)!0.7!(xdp1)$) {$\oplus$};
  \draw[orange, ->] (s) to[bend right=5] (odot1);
  \draw[teal, ->] (t) to[bend right=5] (oplus1);

## ALM

```{r, engine = 'tikz'}
#| eval: false
\usetikzlibrary{positioning}

\def\layersep{3.5cm}

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=\layersep]
    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,fill=black!25,minimum size=17pt,inner sep=0pt]
    \tikzstyle{input neuron}=[neuron, fill=green!50];
    \tikzstyle{output neuron}=[neuron, fill=red!50];
    \tikzstyle{annot} = [text width=4em, text centered]

    % Draw the input layer nodes
    \foreach \name / \y in {1,2}
        \node[input neuron, pin=left:Input \#\y] (I-\name) at (0,-\y) {};

    % Draw the output layer nodes
    \foreach \name / \y in {1,2,3}
        \path[yshift=1.0cm]
            node[output neuron] (O-\name) at (\layersep,-\y cm) {};

    % Connect every node in the input layer with every node in the
    % output layer.
    \foreach \source in {1,2}
        \foreach \dest in {1,2,3}
            \path (I-\source) edge (O-\dest);

    % Annotate the layers with equations
    \node[above of=I-1, node distance=1.5cm] (il) {$a_i(X)=e^{-\gamma \cdot (X-X_i)^2}$ \\ $\frac{a_i(X)}{\sum a_i(X)}$};
    \node[above of=O-1, node distance=1.5cm] (ol) {$O_j(X)=\sum_{i=1}^M w_{j i} \cdot a_i(X)$ \\ $P[Y_j|X]=\frac{O_j(X)}{\sum_{k=1}^L O_k(X)}$};
\end{tikzpicture}

```{r, engine = 'tikz'}
#| eval: false
#| 
\usetikzlibrary{positioning}

\def\layersep{3.5cm}

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=\layersep]
    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,fill=black!25,minimum size=17pt,inner sep=0pt]
    \tikzstyle{input neuron}=[neuron, fill=green!50];
    \tikzstyle{output neuron}=[neuron, fill=red!50];
    \tikzstyle{annot} = [text width=4em, text centered]

    % Draw the input layer nodes
    \foreach \name / \y in {1,2}
        \node[input neuron, pin=left:Input \#\y] (I-\name) at (0,-\y) {$X_{\y}$};

    % Draw the output layer nodes
    \foreach \name / \y in {1,2,3}
        \path[yshift=1.0cm]
            node[output neuron] (O-\name) at (\layersep,-\y cm) {$Y_{\y}$};

    % Connect every node in the input layer with every node in the
    % output layer.
    \foreach \source in {1,2}
        \foreach \dest in {1,2,3}
            \path (I-\source) edge (O-\dest);

    % Annotate the layers with equations
    \node[above of=I-1, node distance=1.5cm] (il) {$a_i(X)=e^{-\gamma \cdot (X-X_i)^2}$ \\ $\frac{a_i(X)}{\sum a_i(X)}$};
    \node[above of=O-1, node distance=1.5cm] (ol) {$O_j(X)=\sum_{i=1}^M w_{j i} \cdot a_i(X)$ \\ $P[Y_j|X]=\frac{O_j(X)}{\sum_{k=1}^L O_k(X)}$};
\end{tikzpicture}

```{r, engine = 'tikz'}
#| eval: false
#| 
\usetikzlibrary{positioning, fit}

\def\layersep{3.5cm}

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=\layersep]
    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,fill=black!25,minimum size=17pt,inner sep=0pt]
    \tikzstyle{input neuron}=[neuron, fill=green!50];
    \tikzstyle{output neuron}=[neuron, fill=red!50];
    \tikzstyle{annot} = [text width=4em, text centered]

    % Draw the input layer nodes
    \foreach \name / \y in {1,2}
        \node[input neuron, pin=left:Input \#\y] (I-\name) at (0,-\y) {$X_{\y}$};

    % Draw the output layer nodes
    \foreach \name / \y in {1,2,3}
        \path[yshift=1.0cm]
            node[output neuron] (O-\name) at (\layersep,-\y cm) {$Y_{\y}$};

    % Connect every node in the input layer with every node in the
    % output layer.
    \foreach \source in {1,2}
        \foreach \dest in {1,2,3}
            \path (I-\source) edge (O-\dest);

    % Annotate the layers with equations
    \node[above of=I-1, node distance=1.5cm] (il) {$a_i(X)=e^{-\gamma \cdot (X-X_i)^2}$ \\ $\frac{a_i(X)}{\sum a_i(X)}$};
    \node[above of=O-1, node distance=1.5cm] (ol) {$O_j(X)=\sum_{i=1}^M w_{j i} \cdot a_i(X)$ \\ $P[Y_j|X]=\frac{O_j(X)}{\sum_{k=1}^L O_k(X)}$};

    % Draw rectangles over the input and output layer nodes
    \node[rectangle, draw=black, inner sep=0.5cm, fit=(I-1) (I-2)] (inputbox) {};
    \node[rectangle, draw=black, inner sep=0.5cm, fit=(O-1) (O-2) (O-3)] (outputbox) {};

\usetikzlibrary{positioning, fit, calc}

\def\layersep{5cm}
\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=\layersep]
    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,fill=black!25,minimum size=17pt,inner sep=0pt]
    \tikzstyle{input neuron}=[neuron, fill=green!50];
    \tikzstyle{output neuron}=[neuron, fill=red!50];
    \tikzstyle{annot} = [text centered]

    % Draw the input layer nodes horizontally
    \foreach \name / \y in {1,2}
        \node[input neuron, pin=left:Input \#\y] (I-\name) at ($(1.5*\y cm,0)$) {$X_{\y}$};

    % Draw the output layer nodes
    \foreach \name / \y in {1,2,3}
        \node[output neuron] (O-\name) at ($(1.5*\name cm, -\layersep)$) {$Y_{\y}$};

    % Connect every node in the input layer with every node in the
    % output layer.
    \foreach \source in {1,2}
        \foreach \dest in {1,2,3}
            \path (I-\source) edge (O-\dest);

    % Add input stimulus symbol above the input layer
    \node[above=2cm of I-1, anchor=south] (input-stimulus) {Stimulus $S$};

    % Add output response symbol below the output layer
    \node[below=2cm of O-2, anchor=north] (output-response) {Response $R$};

    % Annotate the layers with equations
    \node[left=4cm of I-1, anchor=east, font=\small, text width=5cm] (ile) {$a_i(X)=e^{-\gamma \cdot (X-X_i)^2}$ \\ $\frac{a_i(X)}{\sum a_i(X)}$};
    \node[left=4cm of O-1, anchor=east, font=\small, text width=5cm] (ole) {$O_j(X)=\sum_{i=1}^M w_{j i} \cdot a_i(X)$ \\ $P[Y_j|X]=\frac{O_j(X)}{\sum_{k=1}^L O_k(X)}$};

    % Add rectangles around input and output layers
    \node[draw,rectangle,fit=(I-1) (I-2),minimum width=4cm, label=above:Input Layer] (input-rect) {};
    \node[draw,rectangle,fit=(O-1) (O-2) (O-3),minimum width=4cm, label=above:Output Layer] (output-rect) {};

    % Add rectangle for the decoding process
    \node[draw,rectangle,fit=(output-response), label=above:Decoding Process, minimum width=3cm] (decoding-rect) {};

    % Add arrow from output layer to decoding process
    \draw[->,thick] (output-rect) -- (decoding-rect);

### 2023-09-17 Misc/e1_brms_test.qmd
table updates, analysis approach section
sync

test <- readRDS(here("data/e1_08-04-23.rds")) |> 
  filter(expMode2 == "Test") |> 
  mutate(distS2 = custom_scale(dist))

@@

>>>>

test <- readRDS(here("data/e1_08-21-23.rds")) |> 
  filter(expMode2 == "Test") |> 
  mutate(distS2 = custom_scale(dist))

@@

modelName <- "e1_testDistBT_RF"
e1_testDistBT_RF <- brm(dist ~ (condit * vb) + bandType + (1 + vb +bandType|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=2000,chains=4,silent=0,
                      control=list(adapt_delta=0.92, max_treedepth=13))
```
